Oregon_Wildfire_reduced

### 2017-03-02 r_scripts/oregon_clean.rmd
updated summary markdown file to use whole dataset
change to whole data

# import data ------------------------------------------------------------------
# Read in first 200,000 lines for exploration.

read_path <- paste0("../data/gan_episodes_of_care.txt")
oregon_df <- fread(read_path, sep = "|", nrows = 200000, showProgress = T)
fwrite(oregon_df, "../data/oregon_epis_care_reduced.csv")

# I wrote a reduced dataframe of 200,000 rows to get an idea of data structure

# import the reduced dataframe
start_time <- Sys.time()
oregon_df <- fread("../data/oregon_epis_care_reduced.csv", sep = ",", 
                   colClasses = rep("character", 72))
stop_time <-  Sys.time() - start_time

# time it took
stop_time # 1.968219 secs

>>>>

# import data ------------------------------------------------------------------

read_path <- paste0("../data/gan_episodes_of_care.txt")

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # 20 mins
